---
title: "Untitled"
output: html_document
---
## source

```{r setup, include=FALSE}
baseD = "/Users/yigewu/Box\ Sync/"
require(knitr)
opts_knit$set(root.dir = baseD)
setwd(baseD)
source("./cptac2p_analysis/phospho_network/phospho_network_shared.R")
```

## inputs
``` {r vairiables}
num_genoalt_thres <- 4
cancers2proces <- c("BRCA", "OV", "CO", "UCEC", "CCRCC")
```

``` {r input-mut-impact-tab}
mut_impact_tab <- load_mut_impact_proteome()
mut_impact_tab <- mut_impact_tab %>%
  filter(cancer %in% cancers2proces) %>%
  filter(SUB_GENE.is_kinase | SUB_GENE.is_phosphatase | SUB_GENE.is_substrate | SELF == "cis") %>%
  filter(affected_exp_type %in% c("PRO", "PHO")) %>%
  filter(num >= num_genoalt_thres)
mut_impact_tab %>% nrow()
```

## how mutations associate with kinase/substrate abundance levels
### cis effect
``` {r cis}
mut_impact_tab %>%
  filter(SELF == "cis") %>%
  select(GENE) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "cis") %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()

## % associated
mut_impact_tab %>%
  filter(SELF == "cis", p < 0.05) %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()

## % associated
mut_impact_tab %>%
  filter(SELF == "cis", fdr < 0.05) %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "cis", fdr < 0.05) %>%
  arrange(fdr)

## kinases %
mut_impact_tab %>%
  filter(SELF == "cis", p < 0.05) %>%
  filter(GENE %in% kinases) %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "cis", fdr < 0.05) %>%
  filter(GENE %in% kinases) %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()
```

``` {r}
mut_impact_tab %>%
  filter(SELF == "cis", fdr < 0.05) %>%
  # select(pair, cancer,  variant_class, fdr, meddiff) %>%
  filter(affected_exp_type %in% affected_exp_types2process) %>%
  arrange(fdr) %>%
  select(pair_pro_cancer) %>%
  unique
```

``` {r}
## kinases %
mut_impact_tab %>%
  filter(SELF == "cis", p < 0.05) %>%
  filter(GENE %in% phosphatases) %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "cis", fdr < 0.05) %>%
  filter(GENE %in% phosphatases) %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "cis", fdr < 0.05) %>%
    filter(GENE %in% phosphatases)
```
#### affect protein
``` {r cis-protein}
mut_impact_tab %>%
  filter(SELF == "cis") %>%
  filter(affected_exp_type == "PRO") %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "cis", p < 0.05) %>%
  filter(affected_exp_type == "PRO") %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()
```

#### affect phospho
``` {r cis-phospho}
mut_impact_tab %>%
  filter(SELF == "cis") %>%
  filter(affected_exp_type == "PHO") %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "cis", p < 0.05) %>%
  filter(affected_exp_type == "PHO") %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "cis", p < 0.05) %>%
  filter(affected_exp_type == "PHO") %>%
  filter(!(pair_pro_cancer %in% mut_impact_tab$pair_pro_cancer[mut_impact_tab$p < 0.05 & mut_impact_tab$affected_exp_type == "PRO"])) %>%
    filter((pair_pro_cancer %in% mut_impact_tab$pair_pro_cancer[mut_impact_tab$affected_exp_type == "PRO"])) %>%
  select(GENE, cancer) %>%
  unique() %>%
  nrow()
```

``` {r cis-affect-phospho-without-pro-change}
mut_impact_pho_tab <- merge(mut_impact_tab[mut_impact_tab$SUB_MOD_RSD != "PRO",],
                          mut_impact_tab[mut_impact_tab$SUB_MOD_RSD == "PRO", 
                                         c("fdr", "GENE", "SUB_GENE", "cancer", "variant_class", 
                                           "num", "num_control", "p", "meddiff")],
                          by = c("GENE", "SUB_GENE","cancer", "variant_class"), all.x = T, suffixes = c("", ".pro"))


mut_impact_pho_tab %>%
  filter(affected_exp_type %in% affected_exp_types2process) %>%
  filter(SELF == "cis") %>%
  filter(p < 0.05) %>%
  filter(p.pro > 0.05) %>%
  filter(variant_class == "missense") %>%
  # filter(GENE %in% unlist(SMGs)) %>%
  select(pair, cancer, pair, variant_class, 
         fdr, meddiff, num, p,
         fdr.pro, meddiff.pro, num.pro, p.pro) %>%
  arrange(fdr)

mut_impact_pho_tab %>%
  filter(affected_exp_type %in% affected_exp_types2process) %>%
  filter(SELF == "cis") %>%
  filter(fdr < 0.05) %>%
  # filter(p < 0.05) %>%
  filter(p.pro < 0.05) %>%
  # filter(GENE %in% unlist(SMGs)) %>%
  select(pair, cancer, pair, variant_class, 
         fdr, meddiff, num, p,
         fdr.pro, meddiff.pro, num.pro, p.pro) %>%
  arrange(fdr)

mut_impact_pho_tab %>%
  filter(affected_exp_type %in% affected_exp_types2process) %>%
  filter(SELF == "cis") %>%
  filter(p < 0.05) %>%
  filter(p.pro < 0.05) %>%
  mutate(pair_cancer = paste0(pair, ":", cancer)) %>%
  filter(pair_cancer %in% regression$pair_cancer[regression$regulated]) %>%
  select(pair, cancer, pair, variant_class, 
         fdr, meddiff, num, p,
         fdr.pro, meddiff.pro, num.pro, p.pro) %>%
  arrange(fdr)

regression %>%
  filter(pair == "MAP3K1:MAP3K1:S250")

```
### trans effect
``` {r trans-P-sig}
mut_impact_tab %>%
  filter(SELF == "trans") %>%
  select(GENE) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  select(pair_pro) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  select(pair_pro_cancer) %>%
  unique() %>%
  nrow()
1744/9214

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(p < 0.05) %>%
  select(pair_pro_cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.05) %>%
  select(pair_pro_cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(p < 0.05) %>%
  # filter(num >= 10) %>%
  filter(GENE %in% unlist(SMGs)) %>%
  select(GENE) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(p < 0.05) %>%
  # filter(num >= 10) %>%
  filter(GENE %in% unlist(SMGs)) %>%
  select(SUB_GENE) %>%
  unique() %>%
  nrow()

pair_pro_reoccur <- mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(p < 0.05) %>%
  select(pair_pro_cancer, pair_pro, GENE, SUB_GENE) %>%
  unique() %>%
  select(pair_pro, GENE, SUB_GENE) %>%
  table() %>%
  data.frame() %>%
  filter(Freq > 0)

pair_pro_reoccur %>%
  filter(Freq > 1) %>%
  arrange(-Freq)
```

``` {r trans-p-sig-write-table}
for (cancer_tmp in cancers2process) {
  mut_affected_genes_Psig <- mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(p < 0.05) %>%
  filter(cancer == cancer_tmp) %>%
  filter(GENE %in% SMGs[[cancer_tmp]]) %>%
  select(SUB_GENE) %>%
  unique()

  write.table(x = mut_affected_genes_Psig$SUB_GENE, file = paste0(makeOutDir(resultD = resultD), cancer_tmp, "_mut_affected_genes_Psig.txt"),
              col.names = F, row.names = F, sep = "\t", quote = F)
  
mut_affected_genes_background <- mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  filter(GENE %in% SMGs[[cancer_tmp]]) %>%
  select(SUB_GENE) %>%
  unique()
  write.table(x = mut_affected_genes_background$SUB_GENE, file = paste0(makeOutDir(resultD = resultD), cancer_tmp, "_mut_affected_genes_background.txt"),
              col.names = F, row.names = F, sep = "\t", quote = F)
}


```

``` {r trans-fdr-sig}
mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.05) %>%
  arrange(fdr) %>%
  select(GENE) %>%
  unique
# 1	TP53			
# 21	CTNNB1			
# 35	JAK1			
# 49	PIK3R1			
# 50	PTEN			
# 51	AKT1

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.05) %>%
  filter(GENE == "PIK3R1")

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.05) %>%
  arrange(fdr)

omnipath_tab %>%
  filter(SUB_GENE == "PTEN", GENE == "CSNK2A1") 

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.05) %>%
  select(pair_pro_cancer, pair_pro) %>%
  unique() %>%
  select(pair_pro) %>%
  table()

```

#### kinase mutations
``` {r trans-kinase-mutation}
mut_impact_tab %>%
  filter(SELF == "trans") %>%
  select(GENE) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE %in% kinases) %>%
  select(pair_pro_cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE %in% kinases) %>%
  filter(p < 0.05) %>%
  select(pair_pro_cancer) %>%
  unique() %>%
  nrow()
488/2142

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE %in% phosphatases) %>%
  select(pair_pro_cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE %in% phosphatases) %>%
  filter(p < 0.05) %>%
  select(pair_pro_cancer) %>%
  unique() %>%
  nrow()
50/253
```

##### affect sub protein
##### affect sub phospho
#### substrate mutations
``` {r trans-substrate-mutation}
mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(SUB_GENE.is_kinase | SUB_GENE.is_phosphatase) %>%
  select(pair_pro_cancer) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(SUB_GENE.is_kinase | SUB_GENE.is_phosphatase) %>%
  filter(p < 0.05) %>%
  select(pair_pro_cancer) %>%
  unique() %>%
  nrow()
522/2546

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE %in% phosphatases) %>%
  select(pair_pro) %>%
  unique() %>%
  nrow()

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE %in% phosphatases) %>%
  filter(p < 0.05) %>%
  select(pair_pro) %>%
  unique() %>%
  nrow()
```

##### affect kinase protein
##### affect kinase phospho
### summary
#### prevalence
in cis, % associated overall, for kinase, for the substrates we were looking at
in trans, % associated overall, for kinase mutations, for substrate mutations  

### examples
#### TP53
``` {r TP53-FDR}
mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SELF == "trans") %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SELF == "trans") %>%
  filter(SUB_GENE.is_kinase) %>%
  select(SUB_GENE) %>%
  unique()


```

``` {r TP53-kinase-FDR}
pair_pro_reoccur %>%
  filter(GENE == "TP53") %>%
  filter(Freq > 1) %>%
  arrange(-Freq)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SELF == "trans") %>%
  filter(SUB_GENE.is_kinase) %>%
  select(pair_pro, pair_pro_cancer) %>%
  unique() %>%
  select(pair_pro) %>%
  table()

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SUB_GENE %in% c("AURKA", "CHEK2", "EIF2AK2", "SMG1", "STK11")) %>%
  select(cancer, pair, variant_class, fdr, meddiff)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SUB_GENE %in% c("CHEK2")) %>%
  select(cancer, pair, variant_class, fdr, meddiff)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SUB_GENE %in% c("CHEK1")) %>%
  select(cancer, pair, variant_class, fdr, meddiff)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SUB_GENE %in% c("ATR")) %>%
  select(cancer, pair, variant_class, fdr, meddiff)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SUB_GENE %in% c("ATM")) %>%
  select(cancer, pair, variant_class, fdr, meddiff)
```

```{r TP53-ATR}
mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(SUB_GENE %in% c("ATR")) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(SUB_GENE %in% c("ATR")) %>%
  filter(SUB_MOD_RSD == "PRO") %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(SUB_GENE %in% c("ATR")) %>%
  filter(SUB_MOD_RSD == "RNA") %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(SUB_GENE %in% c("TOPBP1", "MSH6", "CLSPN", "ATRIP", "RAD50")) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(SUB_GENE %in% c("RAD50")) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

regression %>%
  filter(SUB_GENE == "ATR" & SUB_MOD_RSD == "T1989") %>%
  filter(regulated == T)

regression %>%
  filter(GENE == "ATR") %>%
  filter(regulated == T) %>%
  filter(Cancer == "BRCA")

regression %>%
  filter(GENE == "ATR") %>%
  filter(regulated == T) %>%
  filter(Cancer == "BRCA") %>%
  filter(!is.na(Source))

regression %>%
  filter(SUB_GENE == "TOPBP1") %>%
  filter(regulated == T) %>%
  filter(Cancer == "BRCA")

```

```{r TP53-CDK1}
mut_impact_tab <- load_mut_impact_proteome()
mut_impact_tab <- mut_impact_tab %>%
  filter(cancer %in% cancers2proces) %>%
  filter(SUB_GENE.is_kinase | SUB_GENE.is_phosphatase | SUB_GENE.is_substrate | SELF == "cis") %>%
  filter(num >= num_genoalt_thres)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  # filter(fdr < 0.05) %>%
  filter(SUB_GENE %in% c("CDK1")) %>%
  select(cancer, pair, variant_class, fdr, meddiff) %>%
  arrange(fdr)
```


``` {r TP53-phosphatase-FDR}
mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SELF == "trans") %>%
  filter(SUB_GENE.is_phosphatase) %>%
  select(pair_pro, pair_pro_cancer) %>%
  unique() %>%
  select(pair_pro) %>%
  table()
# TP53:PPP1CB TP53:PPP2CA TP53:PPP2CB 
#           1           1           1 

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SUB_GENE %in% c("PPP2CA", "PPP2CB")) %>%
  select(cancer, pair, variant_class, fdr, meddiff)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(fdr < 0.05) %>%
  filter(SUB_GENE %in% c("PPP1CB")) %>%
  select(cancer, pair, variant_class, fdr, meddiff)

```


``` {r TP53-correlated}
regression %>%
  filter(SUB_GENE == "TP53") %>%
  filter(fdr_sig == T)

mut_impact_tab %>%
  filter(GENE == "TP53") %>%
  filter(SUB_GENE == "IKBKB")


regression %>%
  filter(GENE == "MAPKAPK5") %>%
    filter(SUB_GENE == "TP53")

regression %>%
  filter(GENE == "AURKA") %>%
  filter(SUB_GENE == "TP53")

```

```{r candidates2write}
mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.05) %>%
  filter(GENE != "TP53") %>%
  filter(SUB_GENE.is_kinase == T | SUB_GENE.is_phosphatase == T| SUB_GENE.is_substrate == T) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)
```
#### JAK1
```{r JAK1}
mut_impact_tab %>%
  filter(SELF == "cis") %>%
  # filter(fdr < 0.05) %>%
  filter(GENE == "JAK1") %>%
  # filter(SUB_GENE.is_kinase == T | SUB_GENE.is_phosphatase == T| SUB_GENE.is_substrate == T) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)

mut_impact_tab %>%
  # filter(SELF == "trans") %>%
  # filter(fdr < 0.05) %>%
  filter(GENE == "JAK1") %>%
  # filter(SUB_GENE.is_kinase == T | SUB_GENE.is_phosphatase == T| SUB_GENE.is_substrate == T) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)

mut_impact_tab %>%
  # filter(SELF == "trans") %>%
  # filter(fdr < 0.05) %>%
  filter(GENE == "STAT3") %>%
  # filter(SUB_GENE.is_kinase == T | SUB_GENE.is_phosphatase == T| SUB_GENE.is_substrate == T) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)

regression %>%
  filter(GENE == "JAK1") %>%
  filter(SUB_GENE == "STAT3")

regression %>%
  filter(GENE == "JAK1")

mut_impact_tab %>%
  filter(GENE == "JAK1") %>%
  filter(SUB_GENE == "STAT3") %>%
  filter(cancer == "UCEC") %>%
  select(cancer, pair, variant_class, num, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE == "JAK1") %>%
  filter(SUB_GENE == "STAT3") %>%
  filter(variant_class == "truncation") %>%
  filter(cancer == "UCEC") %>%
  select(cancer, pair, variant_class, num, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE != "JAK1") %>%
  filter(SUB_GENE == "STAT3") %>%
  filter(cancer == "UCEC") %>%
  select(cancer, pair, variant_class, num, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE == "GATA3") %>%
  # filter(SUB_GENE.is_kinase == T | SUB_GENE.is_phosphatase == T| SUB_GENE.is_substrate == T) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)
```

#### WNT-CTNNB1
``` {r CTNNB1}
mut_impact_tab <- load_mut_impact_proteome()
mut_impact_tab <- mut_impact_tab %>%
  filter(cancer %in% cancers2proces) %>%
  # filter(affected_exp_type %in% c("PRO", "PHO")) %>%
  filter(num >= num_genoalt_thres)

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.05) %>%
  filter(GENE == "CTNNB1") %>%
  filter(SUB_GENE.is_kinase == T | SUB_GENE.is_phosphatase == T| SUB_GENE.is_substrate == T) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.05) %>%
  filter(GENE == "APC") %>%
  filter(SUB_GENE.is_kinase == T | SUB_GENE.is_phosphatase == T| SUB_GENE.is_substrate == T) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p, SUB_GENE.is_kinase, SUB_GENE.is_phosphatase, SUB_GENE.is_substrate) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.1) %>%
  filter(GENE %in% c("CTNNB1", "APC", "AXIN1")) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE %in% c("APC")) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(SELF == "cis") %>%
  filter(GENE %in% c("APC")) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE %in% c("APC")) %>%
  filter(SUB_GENE %in% c("CSNK1A1")) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE %in% c("CTNNB1")) %>%
  filter(SUB_GENE %in% c("PRKCD")) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  # filter(fdr < 0.05) %>%
  filter(GENE == "CTNNB1") %>%
  filter(SUB_GENE %in% c("PRKCD", "CSNK1A1")) %>%
  # filter(SUB_GENE.is_kinase | SUB_GENE.is_phosphatase | SUB_GENE.is_substrate | SELF == "cis") %>%
  select(cancer, pair, variant_class, fdr, meddiff, p) %>%
  arrange(fdr)

regression %>%
  filter(SUB_GENE == "CTNNB1") %>%
  filter(GENE %in% c("PRKCD", "CSNK1A1")) %>%
  filter(Cancer == "UCEC")


regression %>%
  filter(SUB_GENE == "CTNNB1") %>%
  filter(regulated == T) %>%
  filter(Cancer == "UCEC")

regression %>%
  filter(SUB_GENE == "CTNNB1") %>%
  filter(regulated == T) %>%
  filter(Cancer == "CO")

regression %>%
  filter(SUB_GENE == "APC") %>%
  filter(regulated == T)

```


#### PI3K-AKT
``` {r PI3K}
mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.05) %>%
  filter(GENE != "TP53") %>%
  filter(SUB_GENE.is_kinase | SUB_GENE.is_phosphatase | SUB_GENE.is_substrate) %>%
  filter(affected_exp_type %in% affected_exp_types2process) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(fdr < 0.1) %>%
  filter(cancer == "CCRCC")

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE == "PTEN") %>%
  filter(fdr < 0.1)


mut_impact_tab %>%
  filter(SELF == "cis") %>%
  filter(GENE == "PTEN") %>%
  filter(fdr < 0.1)

mut_impact_tab %>%
  filter(SELF == "trans") %>%
  filter(GENE == "AKT1") %>%
  # filter(p < 0.2) %>%
  filter(SUB_GENE %in% c("GSK3B", "BAD")) %>%
  select(cancer, pair, variant_class, fdr, meddiff, p, num) %>%
  arrange(fdr)

mut_impact_tab %>%
  filter(GENE == "PIK3CA") %>%
  filter(fdr < 0.1)

mut_impact_tab %>%
  filter(GENE == "PIK3CA") %>%
  filter(SUB_GENE == "AKT1") %>%
  select(cancer, pair, variant_class, fdr, meddiff, p, num) %>%
  arrange(fdr)

mut_impact_tab %>% 
  filter(GENE == "PIK3R1") %>%
  filter(fdr < 0.1)

mut_impact_tab %>%
  filter(SUB_GENE == "PIK3CA") %>%
  filter(fdr < 0.1)

mut_impact_tab %>%
  filter(SUB_GENE == "PIK3R1") %>%
  filter(fdr < 0.1)
```

```{r Niban}

regression %>%
  filter(SUB_GENE == "FAM129A") %>%
  filter(Cancer == "BRCA")

```
## mutation impact and phosphorylation correlation
how mutation-proteome associations contribute to the quantitative phosphorylation correlation between kinase and substrate pairs
it's most simple if summarize it at kinase-substrate-protein level
```{r input-regression-and-annotate}
regression <- fread(input = paste0(ppnD, "regression/tables/annotate_regression_with_mut_impact/", 
                                     "regression_cptac2p_cptac3_tumor_reg_nonNA20_mut_impact_cancer_specificity_annotated.txt"),
                    data.table = F)
nrow(regression)
```

```{r summary-regression}
summary_df <- data.frame(is_mut.GENE = !is.na(regression$p.GENE), 
                         is_mut_Psig.GENE = (!is.na(regression$p.GENE) & regression$p.GENE < 0.05), 
                         is_mut_fdrsig.GENE = (!is.na(regression$p.GENE) & regression$fdr.GENE < 0.05),
                         is_mut.SUB_GENE = !is.na(regression$p.SUB_GENE), 
                         is_mut_Psig.SUB_GENE = (!is.na(regression$p.SUB_GENE) & regression$p.SUB_GENE < 0.05),
                         is_mut_fdrsig.SUB_GENE = (!is.na(regression$p.SUB_GENE) & regression$fdr.SUB_GENE < 0.05),
                         cancer = regression$Cancer, 
                         SELF = regression$SELF, 
                         regulated = (regression$pair_pro_cancer %in% regression$pair_pro_cancer[regression$regulated]), 
                         id = regression$pair_pro_cancer)
summary_df_uniq <- unique(summary_df)

summary_tab <- data.frame(table(summary_df_uniq[, colnames(summary_df_uniq)[!(colnames(summary_df_uniq) %in% c("id"))]]))
summary_tab <- summary_tab[summary_tab$Freq > 0,]
```

### association
use fisher's test to test association between abundance levels being associated with mutations and being correlated at certain phosphosite
```{r regression-mut-association-trans}
summary_df_uniq <- summary_df_uniq %>%
  mutate(is_mut_Psig = (is_mut_Psig.SUB_GENE | is_mut_Psig.GENE))

summary_df_uniq %>%
  filter(regulated == T) %>%
  filter(is_mut.GENE == T | is_mut.SUB_GENE == T) %>%
    filter(SELF == "trans") %>%
  select(id) %>%
  unique() %>%
  nrow()

fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T | is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  arrange(id) %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")
# not signficant if merge kinase + substrat tgt

fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T) %>%
  filter(SELF == "trans") %>%
  arrange(id) %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

fisher_tab <- summary_df_uniq %>%
  filter(is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  arrange(id) %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

summary_df_uniq %>%
  filter(regulated == T) %>%
  filter(is_mut_fdrsig.GENE == T | is_mut_fdrsig.SUB_GENE == T)

regression %>%
  filter(pair_pro_cancer == "PRKCD:CTNNB1:UCEC")

mut_impact_tab %>%
  filter(pair_pro_cancer == "CTNNB1:PRKCD:UCEC") %>%
  arrange(fdr)

regression %>%
  filter(pair == "PRKCD:CTNNB1:S552")


```

### prevalence
% kinase-substrate protein pairs being correlated among mutationally-associated pairs
```{r regression-mut-prevalence-BRCA}
cancer_tmp <- "BRCA"
fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T | is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")
# not signficant if merge kinase + substrat tgt

cancer_tmp <- "BRCA"
fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

cancer_tmp <- "BRCA"
fisher_tab <- summary_df_uniq %>%
  filter(is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

```

```{r regression-mut-prevalence-OV}
summary_tab %>%
  filter(regulated == T) %>%
  filter(cancer == "OV") %>%
  filter(is_mut.GENE == T | is_mut.SUB_GENE == T) %>%
  select(Freq) %>%
  sum()

summary_df %>%
  filter(regulated == T) %>%
  filter(is_mut_Psig.GENE | is_mut_Psig.SUB_GENE) %>%
  filter(cancer == "OV") %>%
  select(id) %>%
  unique()
```

```{r regression-mut-prevalence-CO}
cancer_tmp <- "CO"
fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T | is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")
# not signficant if merge kinase + substrat tgt

cancer_tmp <- "CO"
fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

cancer_tmp <- "CO"
fisher_tab <- summary_df_uniq %>%
  filter(is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

```

```{r regression-mut-prevalence-UCEC}
cancer_tmp <- "UCEC"
fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T | is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")
# not signficant if merge kinase + substrat tgt

fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

fisher_tab <- summary_df_uniq %>%
  filter(is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

```

```{r regression-mut-prevalence-CCRCC}
cancer_tmp <- "CCRCC"
fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T | is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")
# not signficant if merge kinase + substrat tgt

fisher_tab <- summary_df_uniq %>%
  filter(is_mut.GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

fisher_tab <- summary_df_uniq %>%
  filter(is_mut.SUB_GENE == T) %>%
  filter(SELF == "trans") %>%
  filter(cancer == cancer_tmp) %>%
  arrange(id)  %>%
  select(regulated, is_mut_Psig) %>%
  table()
fisher_tab
fisher.test(fisher_tab, alternative = "greater")

```

### cancer type specificity
#### prevalance
``` {r mut-cancer-specific}
regression %>%
  filter(regulated_uniq == T) %>%
  filter((!is.na(p.GENE) & (p.GENE < 0.05)) | (!is.na(p.SUB_GENE) & p.SUB_GENE < 0.05))
```
#### association
